---
title: "Homework 1"
author: "Yige Bian (yb2591)"
date: 2023-9-22
output: github_document
---

```{r setup, include = FALSE}
Sys.setlocale("LC_TIME", "English")
library(tidyverse)
```

# Problem 1
## Data description
```{r data initialization}
# Load the moderndive library and load the early_january_weather datase
library(moderndive)
data("early_january_weather")
```

*   Variables in the dataset 'early_january_weather' are `r colnames(early_january_weather)`.
    *   The variable `origin` has class `r class(pull(early_january_weather, origin))`
    *   The variable `year` has class `r class(pull(early_january_weather, year))`
    *   The variable `month` has class `r class(pull(early_january_weather, month))`
    *   The variable `day` has class `r class(pull(early_january_weather, day))`
    *   The variable `hour` has class `r class(pull(early_january_weather, hour))`
    *   The variable `temp` has class `r class(pull(early_january_weather, temp))`
    *   The variable `dewp` has class `r class(pull(early_january_weather, dewp))`
    *   The variable `humid` has class `r class(pull(early_january_weather, humid))`
    *   The variable `wind_dir` has class `r class(pull(early_january_weather, wind_dir))`
    *   The variable `wind_speed` has class `r class(pull(early_january_weather, wind_speed))`
    *   The variable `wind_gust` has class `r class(pull(early_january_weather, wind_gust))`
    *   The variable `precip` has class `r class(pull(early_january_weather, precip))`
    *   The variable `pressure` has class `r class(pull(early_january_weather, pressure))`
    *   The variable `visib` has class `r class(pull(early_january_weather, visib))`
    *   The variable `time_hour` has class `r class(pull(early_january_weather, time_hour))`.
*   The dataset 'early_january_weather' has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 
*   The mean temperature is `r mean(pull(early_january_weather, temp))`

